Deeply Virtual Compton Scattering measurement off bound protons

### 2018-11-29 eg6-letters/incoherent/collaboration_comments/clas_comments.tex
more implementation of clas comments
latest correction after the clas comments
minor edit
update the paper after Raphael's suggestions

 - Line 65. Use "Fig. 1".
   \textcolor{blue}{Kept as FIG.1. We show it in the text as shown in the 
      caption.}

@@

 - Line 84. Use "... is the virtual photoproduction differential cross section 
      ...".
   \textcolor{red}{We do not agree here.}

@@

- Line 173. Use "Fig. 2".
     \textcolor{blue}{We keep it as in the caption.}

@@

- Line 183. Use "Fig. 3".
     \textcolor{blue}{We keep it as in the caption.}

@@

- Line 220. Use "Fig. 4".
      \textcolor{blue}{We prefer to keep it as in the caption.}

@@

- Line 231. Use "Fig. 5".
      \textcolor{blue}{We prefer to keep it as in the caption.}

- Line 233. Use "Fig. 4".
      \textcolor{blue}{We prefer to keep it as in the caption.}

@@

- Line 238. Use "Their model used a nuclear spectral function and considers 
   mainly off-shell effects." This is a statement of jargon that is not 
   appropriate for the general PRL audience.  Please reconsider.
      \textcolor{red}{We kept it as it is.}

@@

- Fig. 4. The labels are all too small on this plot (axis labels, titles, plot 
  kinematic labels)
      \textcolor{red}{Will be revised.}

@@

- Line 255. Use "Fig. 6".
      \textcolor{blue}{We prefer to keep it as in the caption.}

@@

- Line 273. Use "Our results are compared ...".
     \textcolor{blue}{Done}
~\\
\item Page 5:\\
 - Fig. 5 caption.\\
   - Line 5. Use "On the middle plot the curves ...".
     \textcolor{blue}{Done}\\
   - Line 6. Use "On the bottom plot the solid ...".
     \textcolor{blue}{Done}\\
   - Line 8. It is not clear what you mean by "enriched region".  
     \textcolor{blue}{They were not detecting the final state hadron and the 
     were separating the coherent from the incoherent DVCS events based on the 
     assumption that the coherent dominates the low $t$ region and the 
     incoherent dominate the high $t$ region, and they avoided calling it pure 
     coherent or incoherent by labeling them as coherent or incoherent enriched 
     regions. }\\
   - Line 8. Use "... [30]; the curves represent ...".
     \textcolor{blue}{Done}
~\\
References:\\
 - End the following references with a period: [2], [28], [29], [30], [31], 
   [32], [33], [34], [38].
     \textcolor{blue}{Done. All the references have been double checked for 
     this.}

@@

\item Since HERMES already measured DVCS BSA on "coherent enriched" and "
   incoherent enriched" event samples off He4, one has to be more careful i) in 
      the use of ''first'' in the abstract and on lines 62 and 270, ii) on the 
      way to quote or qualify ref. [30]. In any case, the way it is done now is 
      not OK if only because Figs 5 and 6 show that there were previous 
      measurements, and this is contradictory with the use of "first". My 
      suggestion would be to keep the word "first" (at the risk of having 
      problems with a referee), except maybe in line 62, to remove the ref 30 
      in line 49 and to add at the end of the paragraph in line 61 the 
      sentence: "The previous (or pioneering?) measurements of DVCS off nuclei, 
      and in particular off 4He, performed at HERMES [30] yielded results with 
      both "coherent enriched" and "incoherent enriched" event samples, hence 
      not fully exclusive, but significant enough to be compared with our 
      results below".
\textcolor{blue}{}

@@

   \item Line 188-192: one wonders what is done with this 6.5\%. If nothing is 
      done, should be stated explicitly and/or justified
\textcolor{blue}{We have corrected our asymmetries for these accidentals.
      }\\
       \textcolor{blue}{This sentence has been added to the paper: Our final 
       asymmetries have been corrected for this contamination in the form
      $A_{LU~corrected}~=~\frac{1}{1-contamination~percentage}~A_{LU~measured}$ 
      }

   \item Figs 2, 3 and 4: tick labels too small.
\textcolor{red}{will be revised.}

@@

\item Page 3, line 159-160: the equations are quite hard to follow, 
   particularly with the braces. It may look better as a displaymath equation.
\textcolor{blue}{Tested. It is not looking much better.}

\item Page 4, figure 4: the font size is way too small!  \textcolor{red}{Will 
   be revised.}

>>>>

 - Line 65. Use "Fig. 1".
   \textcolor{blue}{Done}

@@

 - Line 84. Use "... is the virtual photoproduction differential cross section 
      ...".
   \textcolor{blue}{Done}

@@

- Line 173. Use "Fig. 2".
     \textcolor{blue}{Done}

@@

- Line 183. Use "Fig. 3".
     \textcolor{blue}{Done}

@@

- Line 220. Use "Fig. 4".
      \textcolor{blue}{Done}

@@

- Line 231. Use "Fig. 5".
      \textcolor{blue}{Done}

- Line 233. Use "Fig. 4".
      \textcolor{blue}{Done}

@@

- Line 238. Use "Their model used a nuclear spectral function and considers 
   mainly off-shell effects." This is a statement of jargon that is not 
   appropriate for the general PRL audience.  Please reconsider.
      \textcolor{blue}{Done}

@@

- Fig. 4. The labels are all too small on this plot (axis labels, titles, plot 
  kinematic labels)
      \textcolor{blue}{Done.}

@@

- Line 255. Use "Fig. 6".
      \textcolor{blue}{Done}

@@

- Line 273. Use "Our results are compared ...".
     \textcolor{blue}{Done}
~\\
\item Page 5:\\
 - Fig. 5 caption.\\
   - Line 5. Use "On the middle plot the curves ...".
     \textcolor{blue}{Done}\\
   - Line 6. Use "On the bottom plot the solid ...".
     \textcolor{blue}{Done}\\
   - Line 8. It is not clear what you mean by "enriched region".  
     \textcolor{blue}{This is jargon introduced in their paper. They were not 
     detecting the final state hadron and were separating the coherent from the 
     incoherent DVCS events based on the assumption that the coherent dominates 
     the low $t$ region and the incoherent dominate the high $t$ region, and 
     they avoided calling it pure coherent or incoherent by labeling them as 
     coherent or incoherent enriched regions. }\\
   - Line 8. Use "... [30]; the curves represent ...".
     \textcolor{blue}{Done}
~\\
References:\\
 - End the following references with a period: [2], [28], [29], [30], [31], 
   [32], [33], [34], [38].
     \textcolor{blue}{Done. All the references have been double checked for 
     this.}

@@

\item Since HERMES already measured DVCS BSA on "coherent enriched" and "
   incoherent enriched" event samples off He4, one has to be more careful i) in 
      the use of ''first'' in the abstract and on lines 62 and 270, ii) on the 
      way to quote or qualify ref. [30]. In any case, the way it is done now is 
      not OK if only because Figs 5 and 6 show that there were previous 
      measurements, and this is contradictory with the use of "first". My 
      suggestion would be to keep the word "first" (at the risk of having 
      problems with a referee), except maybe in line 62, to remove the ref 30 
      in line 49 and to add at the end of the paragraph in line 61 the 
      sentence: "The previous (or pioneering?) measurements of DVCS off nuclei, 
      and in particular off 4He, performed at HERMES [30] yielded results with 
      both "coherent enriched" and "incoherent enriched" event samples, hence 
      not fully exclusive, but significant enough to be compared with our 
      results below".
\textcolor{blue}{We took your suggestion. Modified.}

@@

   \item Line 188-192: one wonders what is done with this 6.5\%. If nothing is 
      done, should be stated explicitly and/or justified
\textcolor{blue}{We have corrected our asymmetries for these accidentals.
      equation 6 has been updated to state that.}\\

   \item Figs 2, 3 and 4: tick labels too small.
\textcolor{blue}{Done.}

@@

\item Page 3, line 159-160: the equations are quite hard to follow, 
   particularly with the braces. It may look better as a displaymath equation.
\textcolor{blue}{Updated.}

\item Page 4, figure 4: the font size is way too small!  \textcolor{blue}{Done
   .}

### 2018-11-29 eg6-letters/incoherent/incoherent_prl.tex
update the paper after Raphael's suggestions

In this Letter, we present the first exclusive measurement of the beam-spin 
asymmetry (BSA) in deeply virtual electroproduction of a real photon off a bound 
proton in $^{4}$He. FIG.~\ref{fig:diags} illustrates the leading-twist handbag 
diagram for the DVCS process. In the Bjorken regime, i.e. large virtual photon 
four-momentum squared ($Q^{2}=-q^2=-(k-k^\prime)^2$), and at small invariant 
momentum transfer ($t=(q-q^\prime)^2$), the DVCS scattering process can be 
factorized, leaving the non-perturbative structure of the nucleon to be 
parameterized in terms of four chirally even GPDs: $H$, $E$, $\widetilde{H}$, 
and $\widetilde{E}$, representing the four helicity-spin combinations of the 
quark-nucleon states \cite{Freund_Collins,Ji_Osborne}. Experimentally, we 
measure the squared sum of the Bethe-Heitler (BH) and the DVCS amplitudes. The 
BH process, where the real photon is emitted by the incident or the scattered 
electron rather than the nucleon, dominates the cross section at our 
kinematics. The BSA arises from the interference of these two terms and is 
directly sensitive to the DVCS amplitude that contains the information on the 
GPDs. Using a longitudinally polarized electron beam (L) and an unpolarized 
target (U), the BSA is defined as:
\begin{equation}
  A_{LU} = \frac{d^{5}\sigma^{+} - d^{5}\sigma^{-} }
                {d^{5}\sigma^{+} + d^{5}\sigma^{-}},
    \label{BSA_equation}
  \end{equation}
where $d^{5}\sigma^{+}$($d^{5}\sigma^{-}$) is the photon electroproduction 
differential cross section for a positive (negative) beam helicity.

@@

Further requirements were applied to clean the identified initial set of 
incoherent DVCS events from accidental and physics background events. First, 
events were selected with $Q^{2}$ greater than 1 GeV$^2$ to ensure the 
applicability of the DVCS handbag diagram, and with $\gamma^{*}p$ invariant 
mass ($W=\sqrt{(q+p)^2}$, assuming that the initial proton is at rest) greater 
than 2 GeV to avoid the nucleon resonance region. The squared transferred 
momentum to the recoil proton $t$, calculated from the four-momentum vectors of 
the incoming and outgoing photons, was required to be greater than a minimum 
kinematically allowed value at given $Q^2$ and 
$W$~($t>t_{min}(~=-Q^{2}~\frac{2(1-~x_{B})(1~-~\sqrt{1~+~\epsilon^{2}})~+~\epsilon~^{2}}{4x_{B}(1-x_{B})+\epsilon^{2}}$, 
where $\epsilon^{2}=~\frac{4M^{2}_{p}x^{2}_{B}}{Q^{2}}$ and $M_{p}$ is the 
proton mass). We specifically used the kinematics of the photons to determine 
$t$ because the initial proton kinematics is unknown due to Fermi motion. We 
ensured the exclusivity of the incoherent DVCS events by imposing a series of 
constraints based on the four-momentum conservation in the reaction 
$ep\rightarrow e'p'\gamma$. These kinematical variables are: the coplanarity 
angle $\Delta\phi$ between the ($\gamma,\gamma^*$) and ($\gamma^*$,$p'$) 
planes, the missing energy, mass, and transverse momentum of the $e'\gamma$ and 
$e'p'\gamma$ systems, the missing mass squared of the $e'p'$ system, and the 
angle $\theta$ between the measured photon and the missing momentum of the 
$e'p'$ system. The experimental data for the most relevant exclusivity 
variables are shown in FIG.~\ref{fig:kin-cuts}. Because of the Fermi motion of 
the nucleons in the helium nucleus, these cuts
are slightly wider than those previously used for free proton experiments~%
\cite{Girod:2007aa}. After the corrections discussed below, the asymmetries 
appear to be stable as a function of cut width and we saw no sizable effect 
that could be related to the initial momentum of the nucleons. We also rejected 
events where a $\pi^0$ was identified by the invariant mass of two photons. At 
the end of this selection process, about 30k events passed all the 
requirements; their kinematic distributions are shown in 
FIG.~\ref{fig:kin-coverage}.

@@

The two main backgrounds that contributed to the event sample after the 
exclusivity cuts are due to accidental coincidences and exclusive $\pi^0$ 
production where one of the photons from the $\pi^0$ decay escapes detection.  
The contribution from accidental events, i.e., $e'p'\gamma$ collections with 
particles originating from different electron scatterings, was evaluated to be 
6.5\% by selecting events passing all our selection cuts but originating from 
different vertices. Our final asymmetries have been corrected for this 
contamination in the form of
$A_{LU~\text{corrected}}~=~\frac{A_{LU~\text{measured}}}{1~-~\text{contamination~percentage}}$.  
The $\pi^0$ contamination was estimated using detector simulation and 
experimental data.  From simulation, we calculated the ratio ($R = 
N^{1\gamma}_{sim}/N^{2\gamma}_{sim}$) of the number of $\pi^0$ events that were 
wrongly identified as exclusive $ep\rightarrow e'p'\gamma$ events to the number 
of events correctly identified as exclusive $ep\rightarrow e'p'\pi^0$. Then in 
each kinematical bin and for each beam-helicity state, the $\pi^0$-subtracted 
experimental DVCS events were calculated as $N = N^{ep\rightarrow 
e'p'\gamma}_{exp}- R~N^{ep\rightarrow e'p'\pi^0}_{exp}$, where 
$N^{ep\rightarrow e'p'\gamma}_{exp}$ ($N^{ep\rightarrow e'p'\pi^0}_{exp}$) is 
the number of the experimentally identified $ep\rightarrow e'p'\gamma$ 
($ep\rightarrow e'p'\pi^0$) events.  Depending on the kinematics, we found this 
contamination to be 8 to 10\%.

@@

Experimentally, $A_{LU}$ is defined as
\begin{equation}
A_{LU} = \frac{1}{P_{B}} \frac{N^{+} - N^{-}}{N^{+} + N^{-} },
\end{equation}
where $N^{+}$ and $N^{-}$ are the number of DVCS events for the positive and 
negative beam-helicity states, and $P_{B}$ is the longitudinal beam 
polarization.

@@

Due to limited statistics, the data were binned two-dimensionally into 36 bins.  
That is, four bins in one of the kinematical variable of interest ($Q^{2}$, 
$x_{B}$, or $t$) and then nine bins in the azimuthal angle ($\phi$).   
FIG.~\ref{fig:alu} presents the measured incoherent $A_{LU}$ as a function of 
$\phi$ in bins of $Q^{2}$ (integrated over the full $x_{B}$ and $t$ ranges), 
$x_{B}$ (integrated over the full $Q^{2}$ and $t$ ranges), and $t$ (integrated 
over the full $Q^{2}$ and $x_{B}$ ranges). The curves on the plots are fits of 
the form $\frac{a_{0}~\sin(\phi)}{1+ a_{1}~\cos(\phi)}$.  The main 
contributions to systematic uncertainties on these fits are from the choice of 
the DVCS exclusivity cuts (6\%) and the large bin size (7\%). The systematic 
uncertainties sum up to less than 10\% for all data points and thus always 
remain significantly smaller than the statistical uncertainities.

FIG.~\ref{fig:alu90} presents the dependence of the fitted $A_{LU}$ values at 
$\phi$~=~90$^{\circ}$ ($a_{0}$ parameter from the individual fits in 
FIG.~\ref{fig:alu}) on the kinematical variables $Q^2$, $x_{B}$, and $t$.  
Within the given uncertainties, $A_{LU}$ does not show a strong dependence on 
$Q^2$.  The $x_{B}$ and $t$ dependencies are compared to the theoretical 
calculations performed by S.~Liuti and K.~Taneja \cite{simonetta_2}. Their 
model uses a nuclear spectral function and considers mainly off-shell effects.  
The calculations are carried out at slightly different kinematics than our data 
but still provide important guidance. The experimental results appear to have 
smaller asymmetries especially at small $x_{B}$ than the calculations. These 
differences may arise from nuclear effects that are not taken into account in 
the model, such as long-range interactions and final state interactions of the 
knocked-out proton. On the graph for the $-t$ dependence, we show previous 
measurements by HERMES collaboration \cite{Airapetian:2009cga}, in which only 
electrons and photons were measured. Due to the large experimental 
uncertainties of the HERMES points, the two measurements are completely 
compatible.

@@

One can use the nuclear DVCS to measure a ``generalized'' EMC effect in order 
to see if significant nuclear effects are also visible within the GPD 
framework. To explore this idea, we constructed the ratio of $A_{LU}$ for bound 
protons to that on a free proton target.  
FIG.~\ref{fig:incoh_EMC_ratio_ALU_proton} presents the BSA ratio based on 
interpolation of the free proton asymmetries from CLAS \cite{Girod:2007aa} as a 
function of the kinematical variable $t$. The $A_{LU}$ ratios show 25\%-40\% 
lower asymmetries that are independent of $t$ for a bound proton compared to 
the free proton. The measurements disagree with the off-shell 
\cite{simonetta_2} and the on-shell calculations that use the medium-modified 
GPDs as calculated from the quark-meson coupling model \cite{Guzey:2008fe}. Our 
results show that an important nuclear effect is missing from the existing 
models in order to explain this strong quenching of the BSA. More theoretical 
developments will be needed to identify the origin of this quenching, in 
particular it will be important to differentiate initial from final state 
effects and how they affect the DVCS asymmetries.

>>>>

In this Letter, we present the first exclusive measurement of the beam-spin 
asymmetry (BSA) in deeply virtual electroproduction of a real photon off a 
bound proton in $^{4}$He. Fig.~\ref{fig:diags} illustrates the leading-twist 
handbag diagram for the DVCS process. In the Bjorken regime, i.e. large virtual 
photon four-momentum squared ($Q^{2}=-q^2=-(k-k^\prime)^2$), and at small 
invariant momentum transfer ($t=(q-q^\prime)^2$), the DVCS scattering process 
can be factorized, leaving the non-perturbative structure of the nucleon to be 
parameterized in terms of four chirally even GPDs: $H$, $E$, $\widetilde{H}$, 
and $\widetilde{E}$, representing the four helicity-spin combinations of the 
quark-nucleon states \cite{Freund_Collins,Ji_Osborne}. Experimentally, we 
measure the squared sum of the Bethe-Heitler (BH) and the DVCS amplitudes. The 
BH process, where the real photon is emitted by the incident or the scattered 
electron rather than the nucleon, dominates the cross section at our 
kinematics. The BSA arises from the interference of these two terms and is 
directly sensitive to the DVCS amplitude that contains the information on the 
GPDs. Using a longitudinally polarized electron beam (L) and an unpolarized 
target (U), the BSA is defined as:
\begin{equation}
  A_{LU} = \frac{d^{5}\sigma^{+} - d^{5}\sigma^{-} }
                {d^{5}\sigma^{+} + d^{5}\sigma^{-}},
    \label{BSA_equation}
  \end{equation}
where $d^{5}\sigma^{+}$($d^{5}\sigma^{-}$) is the virtual photoproduction 
differential cross section for a positive (negative) beam helicity.

@@

Further requirements were applied to clean the identified initial set of 
incoherent DVCS events from accidental and physics background events. First, 
events were selected with $Q^{2}$ greater than 1 GeV$^2$ to ensure the 
applicability of the DVCS handbag diagram, and with $\gamma^{*}p$ invariant 
mass ($W=\sqrt{(q+p)^2}$, assuming that the initial proton is at rest) greater 
than 2 GeV to avoid the nucleon resonance region. The squared transferred 
momentum to the recoil proton $t$, calculated from the four-momentum vectors of 
the incoming and outgoing photons, was required to be greater than a minimum 
kinematically allowed value ($t_{min}$) at given $Q^2$ and $W$ defined as: 
\begin{equation}
t_{min} 
   =-Q^{2}~\frac{2(1-~x_{B})(1~-~\sqrt{1~+~\epsilon^{2}})~+~\epsilon~^{2}}{4x_{B}(1-x_{B})+\epsilon^{2}},
\end{equation}
where $\epsilon^{2}=~\frac{4M^{2}_{p}x^{2}_{B}}{Q^{2}}$ and $M_{p}$ is the 
proton mass). We specifically used the kinematics of the photons to determine 
$t$ because the initial proton kinematics is unknown due to Fermi motion. We 
ensured the exclusivity of the incoherent DVCS events by imposing a series of 
constraints based on the four-momentum conservation in the reaction 
$ep\rightarrow e'p'\gamma$. These kinematical variables are: the coplanarity 
angle $\Delta\phi$ between the ($\gamma,\gamma^*$) and ($\gamma^*$,$p'$) 
planes, the missing energy, mass, and transverse momentum of the $e'\gamma$ and 
$e'p'\gamma$ systems, the missing mass squared of the $e'p'$ system, and the 
angle $\theta$ between the measured photon and the missing momentum of the 
$e'p'$ system. The experimental data for the most relevant exclusivity 
variables are shown in Fig.~\ref{fig:kin-cuts}. Because of the Fermi motion of 
the nucleons in the helium nucleus, these cuts
are slightly wider than those previously used for free proton experiments~%
\cite{Girod:2007aa}. After the corrections discussed below, the asymmetries 
appear to be stable as a function of cut width and we saw no sizable effect 
that could be related to the initial momentum of the nucleons. We also rejected 
events where a $\pi^0$ was identified by the invariant mass of two photons. At 
the end of this selection process, about 30k events passed all the 
requirements; their kinematic distributions are shown in 
Fig.~\ref{fig:kin-coverage}.

@@

The two main backgrounds that contributed to the event sample after the 
exclusivity cuts are due to accidental coincidences and exclusive $\pi^0$ 
production where one of the photons from the $\pi^0$ decay escapes detection.  
The contribution from accidental events, i.e., $e'p'\gamma$ collections with 
particles originating from different electron scatterings, was evaluated to be 
6.5\% by selecting events passing all our selection cuts but originating from 
different vertices. The $\pi^0$ contamination was estimated using detector 
simulation and experimental data. From simulation, we calculated the ratio ($R 
= N^{1\gamma}_{sim}/N^{2\gamma}_{sim}$) of the number of $\pi^0$ events that 
were wrongly identified as exclusive $ep\rightarrow e'p'\gamma$ events to the 
number of events correctly identified as exclusive $ep\rightarrow e'p'\pi^0$.  
Then in each kinematical bin and for each beam-helicity state, the 
$\pi^0$-subtracted experimental DVCS events were calculated as $N = 
N^{ep\rightarrow e'p'\gamma}_{exp}- R~N^{ep\rightarrow e'p'\pi^0}_{exp}$, where 
$N^{ep\rightarrow e'p'\gamma}_{exp}$ ($N^{ep\rightarrow e'p'\pi^0}_{exp}$) is 
the number of the experimentally identified $ep\rightarrow e'p'\gamma$ 
($ep\rightarrow e'p'\pi^0$) events. Depending on the kinematics, we found this 
contamination to be 8 to 10\%.

@@

Experimentally, $A_{LU}$ is defined as
\begin{equation}
   A_{LU} = \frac{1}{P_{B}(1-C)} \frac{N^{+} - N^{-}}{N^{+} + N^{-} },
\end{equation}
where $N^{+}$ and $N^{-}$ are the number of DVCS events for the positive and 
negative beam-helicity states, $P_{B}$ is the longitudinal beam polarization, 
and C stands for the contamination percentage of the accidental coincidences.

@@

Due to limited statistics, the data were binned two-dimensionally into 36 bins.  
That is, four bins in one of the kinematical variable of interest ($Q^{2}$, 
$x_{B}$, or $t$) and then nine bins in the azimuthal angle ($\phi$).   
Fig.~\ref{fig:alu} presents the measured incoherent $A_{LU}$ as a function of 
$\phi$ in bins of $Q^{2}$ (integrated over the full $x_{B}$ and $t$ ranges), 
$x_{B}$ (integrated over the full $Q^{2}$ and $t$ ranges), and $t$ (integrated 
over the full $Q^{2}$ and $x_{B}$ ranges). The curves on the plots are fits of 
the form $\frac{a_{0}~\sin(\phi)}{1+ a_{1}~\cos(\phi)}$.  The main 
contributions to systematic uncertainties on these fits are from the choice of 
the DVCS exclusivity cuts (6\%) and the large bin size (7\%). The systematic 
uncertainties sum up to less than 10\% for all data points and thus always 
remain significantly smaller than the statistical uncertainities.

Fig.~\ref{fig:alu90} presents the dependence of the fitted $A_{LU}$ values at 
$\phi$~=~90$^{\circ}$ ($a_{0}$ parameter from the individual fits in 
Fig.~\ref{fig:alu}) on the kinematical variables $Q^2$, $x_{B}$, and $t$.  
Within the given uncertainties, $A_{LU}$ does not show a strong dependence on 
$Q^2$.  The $x_{B}$ and $t$ dependencies are compared to the theoretical 
calculations performed by S.~Liuti and K.~Taneja \cite{simonetta_2}. Their 
model uses a nuclear spectral function and considers mainly the effect of the 
nucleon off-shellness. The calculations are carried out at slightly different 
kinematics than our data but still provide important guidance. The experimental 
results appear to have smaller asymmetries especially at small $x_{B}$ than the 
calculations.  These differences may arise from nuclear effects that are not 
taken into account in the model, such as long-range interactions and final 
state interactions of the knocked-out proton. On the graph for the $-t$ 
dependence, we show previous measurements by HERMES collaboration 
\cite{Airapetian:2009cga}, in which only electrons and photons were measured.  
Due to the large experimental uncertainties of the HERMES points, the two 
measurements are completely compatible.

@@

One can use the nuclear DVCS to measure a ``generalized'' EMC effect in order 
to see if significant nuclear effects are also visible within the GPD 
framework. To explore this idea, we constructed the ratio of $A_{LU}$ for bound 
protons to that on a free proton target.  
Fig.~\ref{fig:incoh_EMC_ratio_ALU_proton} presents the BSA ratio based on 
interpolation of the free proton asymmetries from CLAS \cite{Girod:2007aa} as a 
function of the kinematical variable $t$. The $A_{LU}$ ratios show 25\%-40\% 
lower asymmetries that are independent of $t$ for a bound proton compared to 
the free proton. The measurements disagree with the off-shell 
\cite{simonetta_2} and the on-shell calculations that use the medium-modified 
GPDs as calculated from the quark-meson coupling model \cite{Guzey:2008fe}. Our 
results show that an important nuclear effect is missing from the existing 
models in order to explain this strong quenching of the BSA. More theoretical 
developments will be needed to identify the origin of this quenching, in 
particular it will be important to differentiate initial from final state 
effects and how they affect the DVCS asymmetries.
